Counting infinitely by Oritatami co-transcriptional folding

### 2019-07-17 paper.tex
writting explanation on HA

\subsection{Example of folding}
Let's run an infinite counter from 1 bit width.

\subsubsection{The seed conformation}

>>>>

\subsection{Example of folding first zigzag}
Let's run an infinite counter from 1 bit width.
The seed is encoded with "0", and the starts from bottom row, that is, giving a carry for the least significant bit.

\subsubsection{The first zig pass ($\leftarrow$)}
In Fig, \ref{fig:counter1stzig}, the zig pass folds as follows.
\begin{itemize}
\item{[First module F (Light Green)]} \\Normally, module H is folded above module F, and the seed corresponding to this module H now represents None.
Then, module F forms a shape which represents None and propagates carry equal to 1.
\item{[First module L (Light Blue)]} \\Since the seed here does not have a turn signal, module L forms glider and propagates carry while extending straight.

\item{[First module H (Pink)]} \\The seed is encoded 0 and module folding starts from the bottom row, that is, the carry equal to 1.
Then, HA folds into H01, which represents 1 and is output of carry equal 0.

\item{[First module R (Yellow) and 2nd module F]} \\Both module form glider which start from top row and end to top row, in order to propagate carry equal 0.

\end{itemize}

\subsubsection{The first zag pass ($\rightarrow$)}
In Fig. \ref{fig:counter1stzig}, it is folded until second module F, and module L is transferred as the next transcript.
Fig. \ref{fig:counter1stzag} shows how zag pass is folded.
Now, there is a Turn Signal at the left end of the seed, so L's transcript binds to its signal and loses the shape of glider in order to turn.
In addition, the turned module L forms a Turn Signal at its end.

The zag pass folds as follows.
\begin{itemize}
\item{[module H and module R]} \\Since the module F of last module in zig pass represents None,
module H folds into Hn also representing None. The module R form glider for margin.
\item{[module F, L, and H]} \\There are three types of brick, H01, H10 and He1, representing 1 in module H, and different signals are defined as 1 any. Then, module F folds into brick F1 no matter which module H is above, representing 1. The module L folds glider and the module H folds brick Hn.

\end{itemize}
\begin{figure}[tb]
\centering
\includegraphics[width=\linewidth]{fig/svg/CounterEx5_1.pdf}
\caption{
The first zig pass.
The seed is encoded with "0", and the counter increments it by giving a carry.
Module H outputs "1" as a sum and cancels the carry.
}
\label{fig:counter1stzig}
\end{figure}

\begin{figure}[tb]
\centering
\includegraphics[width=\linewidth]{fig/svg/CounterEx11_1.pdf}
\caption{
Module L turns and start the first zag pass.
Since there is a Turn Signal at the left end of the seed, when the carry is 0, module L turns and at the end of L forms Turn Signal.
In zag pass, module F reads the output of module H and copies it down,
}
\label{fig:counter1stzag}
\end{figure}

\subsection{Conformations of Module H}
The half adder module H forms five different paths as shown in Fig. \ref{fig:halfadders}.
Module H reads the already folded bead (F0 or F1) at above as one of the inputs, and determines the other input depending on the folding starts (top or bottom).
Module H forms four bricks of H00, H01, H10, and H11 for each input.
Then, the bricks outputs the sum as beads of bottom row and also outputs carry depending on whether module H is folded top or bottom except He1.
Brick He1 is the first folded module H after overflow.
Since this counter uses three row of gliders as a self-standing method, module H consisting of 30 beads has an even width, and when it starts folding from the bottom, folding ends at the bottom.
That is why brick He1 ends folding at the bottom and outputs carry equal to 0.
\begin{figure}[h]
\begin{tabular}{c}
 \begin{minipage}{0.5\linewidth}
  \centering
   \includegraphics[width=0.6\linewidth]{fig/svg/H00_1.pdf}
 \end{minipage}

 \begin{minipage}{0.5\linewidth}
  \centering
   \includegraphics[width=0.6\linewidth]{fig/svg/H01_1.pdf}

 \end{minipage}
 \end{tabular}

\begin{tabular}{c}
\ \\
 \begin{minipage}{0.33\linewidth}
  \centering
   \includegraphics[width=0.9\linewidth]{fig/svg/H10_1.pdf}
 \end{minipage}

 \begin{minipage}{0.33\linewidth}
  \centering
   \includegraphics[width=0.9\linewidth]{fig/svg/H11_1.pdf}
 \end{minipage}

  \begin{minipage}{0.33\linewidth}
  \centering
   \includegraphics[width=0.9\linewidth]{fig/svg/He1_1.pdf}

 \end{minipage}
 \end{tabular}
 \caption{The paths of module H in zig pass}
 \label{fig:halfadders}
\end{figure}

\subsection{Example of over flow}

\section{How to implement each module with oritatami system}
Each module changes the output depending on the start position of folding and the environment.
